Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-12 paper/meg_exps.tex
o

We compare B2B to four standard methods: Forward regression, Backward regression, CCA and PLS, as implemented in scikit-learn \citep{sklearn}, and optimized with nested cross-validation over twenty $l2$ regularization parameters logarithmically spaced between $10^{-4}$ and $10^4$ (for regression methods) or 1 to 4 canonical components (for cross-decomposition methods).

>>>>

We compare B2B to four standard methods: Forward regression, Backward regression, CCA and PLS, as implemented in scikit-learn \citep{sklearn} and \citep{bilenko2016pyrcca}, and optimized with nested cross-validation over twenty $l2$ regularization parameters logarithmically spaced between $10^{-4}$ and $10^4$ (for regression and CCA methods) or 1 to 4 canonical components (for PLS).

### 2019-11-12 paper/paper.tex
o

We perform two experiments to evaluate B2B: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography (MEG) dataset.
%
We use scikit-learn's CCA, PLS, and RidgeCV objects to compare B2B against the standard baselines \citep{sklearn}.

>>>>

We perform two experiments to evaluate B2B: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography (MEG) dataset.
%
We use scikit-learn's Partial Least Regression (PLS) and RidgeCV \citep{sklearn} as well as pyrcca' regularized canonical compnent analysis (RegCCA, \citep{bilenko2016pyrcca}) objects to compare B2B against the standard baselines.
